Flatiron cleaning

### 2022-01-06 Rmd/Adjusted weight rdi analysis.Rmd
Create new adjusted weight rmd

# `r emo::ji("spiral_notepad")` This report is using **actual weight**

@@

@@

$$CrCl = \frac{(140 - ageatdx) * weight\_closest\_to\_cycle}{72 * creatinine\_closest\_to\_cycle} * 0.85$$
and is capped at 125.  
<br>

@@

`expected_dose` is:  
-`target_auc` * (`CrCl` + 25)   -> for `drugname` == "carboplatin"  
-`BSA` * `target_auc`           -> for `drugname` == "taxel" or "cisplatin"  
(Again keep in mind that `target_auc` is just the name of the column in the data but is calculated differently depending of the drug name)  
It was capped to 900 when was > 900 for a `target_auc` of 6 and to 750 when was > 750 for a `target_auc` of 5 (Carboplatin).

@@

Then I calculate $$relative\ dose\ intensity\ (RDI) = \frac{amount\ given}{expected\ dose}$$

@@

  mutate(relative_dose_intensity = amount / expected_dose # adjusted_expected_dose
  ) %>%
  # select(patientid,linenumber, linenumber_new, chemotherapy_type, drugname_type, drugname,
  #        relative_dose_intensity, linenumber_adj) %>%

@@

# Consort diagram

```{r consort, fig.width=12}
library(ggconsort)
study_cohorts <- 
  Frontline_adjusted %>%
  cohort_start("**Assessed for eligibility**") %>%
  # Define cohorts using named expressions
  # Notice that you can use previously defined cohorts in subsequent steps
  cohort_define(
  flatiron_rec = .full %>% filter(is.na(flatiron_rules)),

  study_criteria = flatiron_rec  %>% 
    filter(!is.na(histology)) %>%
    filter(!is.na(surgerydate)) %>%
    filter(had_carbo_pacli == "Yes") %>% 
    filter(treatment_sequence == "neo + surg + adj" |
             treatment_sequence == "surg + adj") %>%
    filter(is.na(line_keep)),

    missing_data = study_criteria  %>% 
    filter(!(issurgery == "Yes" & is.na(surgerydate))) %>%
    filter(is.na(gap_surg_drugs)) %>%
    filter(days_at_first_drug >= 0 &
             (is.na(surgerydate) | days_at_surg >= 0)) %>%
    filter((
      therapy == "Upfront Chemo" &
        (!is.na(RDI_carbo_neo) & !is.na(RDI_pacli_neo) & 
           !is.na(RDI_carbo_adj) & !is.na(RDI_pacli_adj)) 
    ) | (
      therapy == "Upfront Surgery" &
        (!is.na(RDI_carbo_adj) & !is.na(RDI_pacli_adj))
    )
    ),

    standard_care = missing_data %>% 
    filter(is.na(neo_more_more_than_1line)) %>%
    filter(is.na(frontline_has_maintenance)) %>%
    filter(is.na(too_many_cycle)) %>% 
    filter(is.na(wrong_pacli_dosedense)) %>%
    filter(is.na(switch_drugs)),

    Frontline = standard_care,

  # anti_join is useful for counting exclusions -------------
    excluded1 = anti_join(.full, flatiron_rec, by = "patientid"),
    excluded2 = anti_join(flatiron_rec, study_criteria, by = "patientid"),
    excluded3 = anti_join(study_criteria, missing_data, by = "patientid"),
    excluded4 = anti_join(missing_data, standard_care, by = "patientid")
  ) %>%
  # Provide text labels for cohorts
  cohort_label(
    excluded1 = "excluded albeit flatiron recommendation",
    excluded2 = "<span style='color:darkblue'>no study criteria</span>",
    excluded3 = "<span style='color:darkblue'>no missing_data</span>",
    excluded4 = "<span style='color:darkblue'>no standard_care</span>",
    flatiron_rec = "**Fit flatiron rec**",
    study_criteria = "**Fit study criteria**",
    missing_data = "**Non missing data**",
    Frontline = "**Population Study**"
  )

study_consort <- study_cohorts %>%
  consort_box_add(
    "full", 0, 40, cohort_count_adorn(study_cohorts, .full)
  ) %>%
  consort_box_add(
    "exc_flatiron_rec", 0.2, 35, glue::glue(
      "{cohort_count_adorn(study_cohorts, excluded1)}<br> 
      • <span style='color:darkgreen'>**90 days rule between diagnosis and treatment**</span> <br>
      • 30 days rule excluding patient who didn't survive <br> for at least 30 days after diagnosis <br>
      • Borderline cases (not invasive ovarian cancer) <br>
      • (Data from one PracticeID) <br>
      • (historical structured data were not available for <br> patients seen at academic sites prior to 2015)
      ")
  ) %>%
  consort_box_add(
    "flatiron_rec", 0, 30, cohort_count_adorn(study_cohorts, flatiron_rec)
  ) %>%
  consort_box_add(
    "exc_study_criteria", 0.2, 25, glue::glue(
      "{cohort_count_adorn(study_cohorts, excluded2)}<br> 
      • exclude patients whose histology is unknown <br>
      • remove chemotherapy only patients <br>
      • include only patients who received platin and/or taxane <br>
      • exclude patients who only received neo + surgery <br>
      • include patients with single or dual P/T +/- Bev as frontline treatment
      ")
  ) %>%
  consort_box_add(
    "study_criteria", 0, 20, cohort_count_adorn(study_cohorts, study_criteria)
  ) %>%
  consort_box_add(
    "exc_missing_data", 0.2, 15, glue::glue(
      "{cohort_count_adorn(study_cohorts, excluded3)}<br> 
      • exclude the patients who had surgery but we don’t have a date of surgery -> NONE removed anymore <br> 
      • remove patients with long gap between surgery and adjuvant start (3 months) -> NONE removed anymore <br> 
      • exclude patients with a date of drug or date of surgery BEFORE diagnosis will be excluded (inclined to be wrongly recorded) <br> 
      • exclude patients for whose no RDI were available
      ")
  ) %>%
  consort_box_add(
    "missing_data", 0, 10, cohort_count_adorn(study_cohorts, missing_data)
  ) %>%
  consort_box_add(
    "exc_standard_care", 0.2, 5, glue::glue(
      "{cohort_count_adorn(study_cohorts, excluded4)}<br> 
      • exclude patients with more than 1 line as Neo <br> 
      • exclude patients with maintenance within their frontline <br> 
      • exclude patients with more than 6 cycles in Neo, more than 9 cycles total in upfront chemo or more than 9 cycles in upfront surgery
      ")
  ) %>%
  consort_box_add(
    "Frontline", 0, 0, cohort_count_adorn(study_cohorts, Frontline)
  ) %>%

  consort_arrow_add(
    end = "exc_flatiron_rec", end_side = "left", start_x = 0, start_y = 35
  ) %>%
  consort_arrow_add(
    end = "exc_study_criteria", end_side = "left", start_x = 0, start_y = 25
  ) %>%
  consort_arrow_add(
    end = "exc_missing_data", end_side = "left", start_x = 0, start_y = 15
  ) %>%
  consort_arrow_add(
    end = "exc_standard_care", end_side = "left", start_x = 0, start_y = 5
  ) %>%
  consort_arrow_add(
    end = "Frontline", end_side = "top", start_x = 0, start_y = 40
  )

study_consort %>%
  ggplot() + 
  geom_consort() +
  theme_consort(margin_h = c(1,6), margin_v = c(0,30))
```

>>>>

# `r emo::ji("spiral_notepad")` This report is using **adjusted weight**

@@

ideal_weight is calculated :
- height <= 1.524               ~ 45.5 + 2.3,
- height > 1.524                ~ 45.5 + (2.3 * (((`height` - 1.524) / 0.0254)))

adjusted_weight :
- ((`weight` - `ideal_weight`) * 0.40) + `ideal_weight`

actual_bmi = weight / (height * height)

@@

IF actual_bmi >= 25 :
$$CrCl = \frac{(140 - ageatdx) * weight\_closest\_to\_cycle}{72 * creatinine\_closest\_to\_cycle} * 0.85$$
IF actual_bmi < 25 :

$$adjusted\_CrCl = \frac{(140 - ageatdx) * adjusted\_weight\_closest\_to\_cycle}{72 * creatinine\_closest\_to\_cycle} * 0.85$$
In both cases CrCl is capped at 125.  
<br>

@@

<!-- mutate(adjusted_expected_dose = case_when( -->
<!--     drugname == "carboplatin"                 ~ target_auc * (adjusted_CrCl + 25), -->
<!--     drugname == "paclitaxel"                  ~ BSA * target_auc  -->
<!--     # F19EBBFC60652 Can we fill target_auc? No depends of the type of cycle, or maybe by grouping by cycle type and drug -->
<!--   )) %>%  -->
<!--   mutate(adjusted_expected_dose = case_when( -->
<!--     adjusted_expected_dose > 900 & -->
<!--       target_auc == 6              ~ 900, -->
<!--     adjusted_expected_dose > 750 & -->
<!--       target_auc == 5              ~ 750, -->
<!--     TRUE                           ~ adjusted_expected_dose -->
<!--   )) -->

`adjusted_expected_dose` is:  
-`target_auc` * (`adjusted CrCl` + 25)   -> for `drugname` == "carboplatin"  
-`BSA` * `target_auc`                    -> for `drugname` == "paclitaxel"
(Again keep in mind that `target_auc` is just the name of the column in the data but is calculated differently depending of the drug name)  
It was capped to 900 when was > 900 for a `target_auc` of 6 and to 750 when was > 750 for a `target_auc` of 5 (Carboplatin).

@@

<!-- relative_dose_intensity = amount / adjusted_expected_dose -->

Then I calculate $$relative\ dose\ intensity\ (RDI) = \frac{amount\ received}{adjusted\ expected\ dose}$$

@@

  mutate(relative_dose_intensity = amount / adjusted_expected_dose # adjusted_expected_dose
  ) %>%
  # select(patientid,linenumber, linenumber_new, chemotherapy_type, drugname_type, drugname,
  #        relative_dose_intensity, linenumber_adj) %>%

@@

### 2022-01-06 Rmd/Adjusted weight rdi analysis1.Rmd
Create new adjusted weight rmd

**We have `r clinical_data %>% distinct(patientid) %>% nrow()` patients info in clinical data.  
We have `r drugs %>% distinct(PatientID) %>% nrow()` patients info in drug data.**

```{r drugs episode cleanup}
drugs <- drugs %>% 
  `colnames<-`(str_to_lower(colnames(.))) %>% 
  # Select only records for administration
  filter(episodedatasource == "Administrations") %>%
  # bind with clinical
  inner_join(., clinical_data, 
          by = "patientid") %>% 
  arrange(patientid, episodedate)
```
**But when merged both data, we have `r drugs %>% distinct(patientid) %>% nrow()` patients with clinical information who received drugs.**

@@

- Exclude patients that received wrong dose dense of 1 carbo + 2 paclitaxel
```{r}
standard_care <- standard_care %>% 
  filter(is.na(wrong_pacli_dosedense))

@@

# test <- Frontline %>% 
#   filter(wrong_pacli_dosedense == "exclude")
# 
# wrong_pacli_dosedense <- Treatment %>% arrange(patientid, episodedate, drugname) %>% 
#   filter(str_detect(patientid, paste(test$patientid, collapse = "|"))) %>% 
#   select(patientid, chemotherapy_type, therapy, episodedate, drugname, ismaintenancetherapy, linenumber_new, cycle_increment, too_many_cycle, dose_dense, wrong_pacli_dosedense,  linename)
```
**We have `r standard_care %>% distinct(patientid) %>% nrow()` patients.**

@@

```{r}
Frontline <- standard_care %>%
  filter(is.na(switch_drugs))
```

@@

### For Upfront Chemo
```{r}
data <- Frontline %>% 
  filter(therapy == "Upfront Chemo") %>% 
  select(patientid, month_at_os, vital_status, 
         raceeth, diagnosisdate, surgerydate,
         ageatdx, stagecat, debulking, histology,
         RDI_carbo_neo, RDI_pacli_neo, 
         RDI_carbo_adj, RDI_pacli_adj
         # therapy
  )
nonimp_cox_model <-
  coxph(Surv(month_at_os, vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology,
        data = data)
nonimp_cox_model

@@

### For Upfront Surgery
```{r}
data <- Frontline %>% 
  filter(therapy == "Upfront Surgery") %>% 
  select(patientid, month_at_os, vital_status, 
         raceeth, diagnosisdate, surgerydate,
         ageatdx, stagecat, debulking, histology,
         RDI_carbo_adj, RDI_pacli_adj
         # therapy
  )
nonimp_cox_model <-
  coxph(Surv(month_at_os, vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology,
        data = data)
nonimp_cox_model

@@

# Frontline <- 
#   full_join(Frontline, imputed_data %>% 
#               select(patientid, starts_with("imp_")), 
#             by = "patientid") 
Frontline <- 
  full_join(Frontline, imputed_data %>% 
              select(patientid, starts_with("imp_")), 
            by = "patientid") 
```

@@

@@

<span style="color:green">**Table  Summary of the expected, actual dose, and RDI**</span>
```{r Summary of the expected, actual dose, and RDI}
rdi_study <- 
  RDI_data %>% 
  filter(str_detect(patientid, paste(Frontline$patientid, collapse = "|"))) %>% 
  arrange(patientid, episodedate, drugname) %>% 
  mutate(chemotherapy_type = factor(chemotherapy_type))

@@

## 2.RDI summary table

@@

>>>>

**We have `r clinical_data %>% distinct(patientid) %>% nrow()` patients info in clinical data.  
**We have `r drugs %>% distinct(PatientID) %>% nrow()` patients info in drug data.

```{r drugs episode cleanup}
drugs <- drugs %>% 
  `colnames<-`(str_to_lower(colnames(.))) %>% 
  # Select only records for administration
  filter(episodedatasource == "Administrations") %>%
  # bind with clinical
  inner_join(., clinical_data, 
          by = "patientid") %>% 
  arrange(patientid, episodedate)
```
But when merged both data, we have `r drugs %>% distinct(patientid) %>% nrow()` patients with clinical information who received drugs.

@@

- Exclude patients that received wrong dose dense of 1 carbo + 2 paclitaxel
```{r}
Frontline_adjusted <- standard_care %>% 
  filter(is.na(wrong_pacli_dosedense))

@@

# test <- Frontline %>% 
#   filter(wrong_pacli_dosedense == "exclude")
# 
# wrong_pacli_dosedense <- Treatment %>% arrange(patientid, episodedate, drugname) %>% 
#   filter(str_detect(patientid, paste(test$patientid, collapse = "|"))) %>% 
#   select(patientid, chemotherapy_type, therapy, episodedate, drugname, ismaintenancetherapy, linenumber_new, cycle_increment, too_many_cycle, dose_dense, wrong_pacli_dosedense,  linename)
```
**We have `r Frontline_adjusted %>% distinct(patientid) %>% nrow()` patients.**

@@

<!-- Patients left: -->
```{r}
Frontline_adjusted <- Frontline_adjusted %>%
  filter(is.na(switch_drugs))
```

@@

### For Upfront Chemo
```{r}
data <- Frontline_adjusted %>% 
  filter(therapy == "Upfront Chemo") %>% 
  select(patientid, month_at_os, vital_status, 
         raceeth, diagnosisdate, surgerydate,
         ageatdx, stagecat, debulking, histology,
         RDI_carbo_neo, RDI_pacli_neo, 
         RDI_carbo_adj, RDI_pacli_adj
         # therapy
  )
nonimp_cox_model <-
  coxph(Surv(month_at_os, vital_status) ~ RDI_carbo_neo + RDI_pacli_neo + RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology,
        data = data)
nonimp_cox_model

@@

### For Upfront Surgery
```{r}
data <- Frontline_adjusted %>% 
  filter(therapy == "Upfront Surgery") %>% 
  select(patientid, month_at_os, vital_status, 
         raceeth, diagnosisdate, surgerydate,
         ageatdx, stagecat, debulking, histology,
         RDI_carbo_adj, RDI_pacli_adj
         # therapy
  )
nonimp_cox_model <-
  coxph(Surv(month_at_os, vital_status) ~ RDI_carbo_adj + RDI_pacli_adj + raceeth + ageatdx + stagecat + debulking + histology,
        data = data)
nonimp_cox_model

@@

# Frontline <- 
#   full_join(Frontline, imputed_data %>% 
#               select(patientid, starts_with("imp_")), 
#             by = "patientid") 
Frontline_adjusted <- 
  full_join(Frontline_adjusted, imputed_data %>% 
              select(patientid, starts_with("imp_")), 
            by = "patientid") 
```

@@

# Consort diagram

```{r consort}
library(ggconsort)
study_cohorts <- 
  Frontline_adjusted %>%
  cohort_start("Assessed for eligibility") %>%
  # Define cohorts using named expressions
  # Notice that you can use previously defined cohorts in subsequent steps
  cohort_define(
  flatiron_rec = .full %>% filter(is.na(flatiron_rules)),

  study_criteria = flatiron_rec  %>% 
    filter(!is.na(histology)) %>%
    filter(!is.na(surgerydate)) %>%
    filter(had_carbo_pacli == "Yes") %>% 
    filter(treatment_sequence == "neo + surg + adj" |
             treatment_sequence == "surg + adj") %>%
    filter(is.na(line_keep)),

    missing_data = study_criteria  %>% 
    filter(!(issurgery == "Yes" & is.na(surgerydate))) %>%
    filter(is.na(gap_surg_drugs)) %>%
    filter(days_at_first_drug >= 0 &
             (is.na(surgerydate) | days_at_surg >= 0)) %>%
    filter((!is.na(RDI_carbo_neo) & !is.na(RDI_pacli_neo) &
              !is.na(RDI_carbo_adj) & !is.na(RDI_pacli_adj) &
              therapy == "Upfront Chemo") |
             (!is.na(RDI_carbo_adj) & !is.na(RDI_pacli_adj &
               therapy == "Upfront Surgery"))),

    standard_care = missing_data %>% 
    filter(is.na(neo_more_more_than_1line)) %>%
    filter(is.na(frontline_has_maintenance)) %>%
    filter(is.na(too_many_cycle)),

  Frontline = standard_care %>% 
    filter(is.na(wrong_pacli_dosedense)),
  Frontline1 = Frontline %>%
    filter(is.na(switch_drugs))
  ) %>%
  # Provide text labels for cohorts
  cohort_label(
    flatiron_rec = "**flatiron_rec**",
    study_criteria = "*study_criteria*",
    missing_data = "missing_data",
    standard_care = "standard_care",
    Frontline = "Frontline",
    Frontline1 = "Population Study"
  )
study_cohorts

study_consort <- study_cohorts %>%
  consort_box_add(
    "full", 0, 50, cohort_count_adorn(study_cohorts, .full)
  ) %>%
  consort_box_add(
    "flatiron_rec", 5, 45, glue::glue(
      "{cohort_count_adorn(study_cohorts, flatiron_rec)}<br> 
      • <span style='color:darkgreen'>**90 days rule between diagnosis and treatment**</span> <br>
      • 30 days rule excluding patient who didn't survive <br> for at least 30 days after diagnosis <br>
      • Borderline cases (not invasive ovarian cancer) <br>
      • Data from one PracticeID <br>
      • historical structured data were not available for <br> patients seen at academic sites prior to 2015
      ")

  ) %>%
  consort_box_add(
    "study_criteria", 5, 35, cohort_count_adorn(study_cohorts, study_criteria)
  ) %>%
  consort_box_add(
    "missing_data", 5, 30, cohort_count_adorn(study_cohorts, missing_data)
  ) %>%
  consort_box_add(
    "standard_care", 5, 25, cohort_count_adorn(study_cohorts, standard_care)
  ) %>%
  consort_box_add(
    "Frontline", 5, 20, cohort_count_adorn(study_cohorts, Frontline)
  ) %>%
  consort_box_add(
    "Frontline1", 0, 15, cohort_count_adorn(study_cohorts, Frontline1)
  ) %>%

  consort_arrow_add(
    end = "flatiron_rec", end_side = "left", start_x = 0, start_y = 45
  ) %>%
  consort_arrow_add(
    end = "study_criteria", end_side = "left", start_x = 0, start_y = 35
  ) %>%
  consort_arrow_add(
    end = "missing_data", end_side = "left", start_x = 0, start_y = 30
  ) %>%
  consort_arrow_add(
    end = "standard_care", end_side = "left", start_x = 0, start_y = 25
  ) %>%
  consort_arrow_add(
    end = "Frontline", end_side = "left", start_x = 0, start_y = 20
  ) %>%
  consort_arrow_add(
    end = "Frontline1", end_side = "top", start_x = 0, start_y = 50
  )

study_consort %>%
  ggplot() + 
  geom_consort() +
  theme_consort(margin_h = 18, margin_v = 1)
```

@@

<span style="color:green">**Table  Summary of the expected, actual dose, and RDI**</span>
```{r Summary of the expected, actual dose, and RDI}
rdi_study <- 
  RDI_data %>% 
  filter(str_detect(patientid, paste(Frontline_adjusted$patientid, collapse = "|"))) %>% 
  arrange(patientid, episodedate, drugname) %>% 
  mutate(chemotherapy_type = factor(chemotherapy_type))

@@

## 1.RDI summary table

@@

           "histology", "stagecat", imp_stagecat,
